ECCCos from the Black Box:\\ Faithful Explanations through\\ Energy-Constrained Conformal Counterfactuals

### 2023-09-25 paper/body.tex
tired

\begin{figure}
  \centering
  \includegraphics[width=1.0\linewidth]{../www/mnist_benchmark.png}
  \caption{Counterfactuals for turning a 3 into a 5: factual (left); then from left to right the counterfactuals generated using \textit{ECCCo}, \textit{ECCCo+}, \textit{REVISE}, \textit{Schut} and \textit{Wachter}.}\label{fig:mnist-bmk}
\end{figure}

>>>>

\begin{figure}
  \centering
  \includegraphics[width=1.0\linewidth]{../www/mnist_benchmark.png}
  \caption{Counterfactuals for turning a 3 into a 5: factual (left), then the counterfactuals generated by \textit{ECCCo}, \textit{ECCCo+}, \textit{REVISE}, \textit{Schut} and \textit{Wachter}.}\label{fig:mnist-bmk}
\end{figure}
